---
title: "TidyTuesday - The Office"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Overview

Working through an old (2020-03-17) [TidyTuesday posting on The Office](https://github.com/rfordatascience/tidytuesday/blob/master/data/2020/2020-03-17/readme.md).

The posted TidyTuesday data are included in a single csv, available via *tidytuesdayR::tt_load().* The post also directs users to the [schrute](https://bradlindblad.github.io/schrute/index.html) package, available on CRAN. The package is simply a means for accessing the complete transcripts, along with the rating information (there's literally a single function in the package - *schrute::theoffice*). For this project, I'm going to use the full transcripts + ratings.

```{r, eval=FALSE}

# Ratings / basic episode info only
# library(tidytuesdayR)
# tt <- tt_load('2020-03-17')

# Ratings / episode info / full transcripts
library(schrute)
df_transcripts <- theoffice

```

## Note

This is my take on the data before checking out Julia Silge's or David Robinson's TidyTuesday entries.
